Lessons Learned for JWST Transiting Planet Time Series from Ground-based Studies of the NIRCam Detectors

### 2018-12-07 ms.tex
more info on GL dewar tests.

Table \ref{tab:testSummary} shows a summary of the ground-based tests that were performed on NIRCam detectors.
The flight NIRCam detectors, controllers, electronics, optics and instrument hardware were used in the Cryogenic Vacuum 3 (CV3) Test 3 as well as OTIS (Optical Telescope Element and Integrated Science).
The GL dewar experiments used flight detectors, but a different controller (Leach).
The Asic dewar located at Steward Observatory in Tucson, Arizona used a spare NIRCam detector, a spare asic controller and the flight software, but no flight optics.

@@

\subsection{GL Dewar Tests}
At the University of Arizona, there is a laboratory setup for assessing NIRCam flight and spare detectors.
The key difference with the Asic dewar is that the detector readout electronics are completely different, using a Leach system that is operated outside of the dewar as opposed to the Asic, which is lives right next to the detectors.
The GL dewar detector stability tests are helpful in isolating noise sources that arise from the detectors versus the readout electronics.

@@

>>>>

Table \ref{tab:testSummary} shows a summary of the ground-based tests that were performed on NIRCam detectors.
The flight NIRCam detectors, controllers, electronics, optics and instrument hardware were used in the Cryogenic Vacuum 3 (CV3) Test 3 as well as OTIS (Optical Telescope Element and Integrated Science).
There were two dewars at the Steward Observatory at the University of Arizona used for time series stability tests.
The GL dewar experiments used flight-like detectors, but a different controller (Leach).
The Asic dewar located at Steward Observatory in Tucson, Arizona used a spare NIRCam detector, a spare asic controller and the flight software, but no flight optics.
These two different kinds of detector electronics can be compared against each other to help isolate detector-related systematics from readout electronics-related systematics.

@@

\subsection{GL Dewar Tests}

The GL dewar, located at the University of Arizona, is a laboratory setup for assessing NIRCam flight and spare detectors.
The key difference with the Asic dewar discussed below is that the detector readout electronics are completely different, using a Leach system that is operated outside of the dewar as opposed to the Asic, which is lives right next to the detectors.
The GL dewar detector stability tests are helpful in isolating noise sources that arise from the detectors versus the readout electronics.

An LED illumination source is pointed at the detectors and the arrays are read out in subarray mode.
Figure \ref{fig:GLtSeries} shows the detector subarray illumination as well as two apertures that were used for time series photometry.
The first handful of frames show an initial "warmup" period lasting about 9 seconds.
This quickly stabilizes to a 1200 ppm level likely dominated by lamp variations.
If one divides the two apertures by each other, the resulting time series is very flat and stable to with 260 ppm.
When binning the data into 2.5 minute increments, the standard deviation is only 51 ppm.

@@

\subsection{Asic Dewar Tests}
